---
title: "Untitled"
output: html_document
---
```{r}
#install.packages("Seurat")
remove.packages('reticulate')
library(reticulate)
remove.packages('Seurat')

install.packages('Seurat')

library(Seurat)
```

```{r}
library(Seurat)
library(ggplot2)
library(readr)
library(readxl)
library(Matrix)
library(tidyr)
library(dplyr)
library(readxl)
library(cowplot)
#library(harmony)
outputDIR = "/data/exx/SC/SC145/Figure.CQS"


list.files()


```

```{r}
samplePDX <- read_xlsx("/home/qcai1/Downloads/SC145/PDX_scRNA_WES_info.xlsx", sheet = 1)
unique(as.character(samplePDX$scSeqName))
data.frame(samplePDX)
```
```{r}
workDIR = "/data/exx/SC/SC145/scPDX_10X_human/"  
allSampleName = list.files(workDIR)

initialSampleName = "S10"
allSampleName = allSampleName[!allSampleName %in% initialSampleName]


fileDIR1 = paste(workDIR, initialSampleName, "/outs/filtered_feature_bc_matrix", sep="")  #S10
Data_tmp<-Read10X(data.dir = fileDIR1)


Object1 <- CreateSeuratObject(counts = Data_tmp, project = initialSampleName, min.cells = 3, min.features=200)
Object1

i <- initialSampleName


Object1@meta.data$Pt <-    samplePDX[samplePDX$scSeqName %in% i,]$Pt   ######################################
Object1@meta.data$sample <-    samplePDX[samplePDX$scSeqName %in% i,]$scSeqName
Object1@meta.data$Newname <-    samplePDX[samplePDX$scSeqName %in% i,]$Newname
Object1@meta.data$HumanMouse <-    samplePDX[samplePDX$scSeqName %in% i,]$HumanMouse
Object1@meta.data$PDXmodel <-    samplePDX[samplePDX$scSeqName %in% i,]$PDXmodel

Object1[["percent.mt"]] <- PercentageFeatureSet(Object1, pattern = "^MT-")
outputName12 = paste0(outputDIR,"/qc/", initialSampleName, ".VlnPlot_before_filter.png")
                                                      #pp = CombinePlots(plots = list(plot1, plot2))
png(outputName12,height =480, width = 960) 
print(VlnPlot(Object1, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3))
dev.off()

Object1 <- NormalizeData(Object1)
Object1 <- FindVariableFeatures(Object1, selection.method = "vst", nfeatures= 2000)
Object1 <- ScaleData(Object1)

Object1 <- subset(Object1, subset = nFeature_RNA > 200 & nFeature_RNA < 6000 & percent.mt < 10)
Object1

outputName12 = paste0(outputDIR,"/qc/", initialSampleName, ".VlnPlot_after.png")
png(outputName12,height =480, width = 960)  
print(VlnPlot(Object1, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3))
dev.off()

```

```{r, echo=False}
Object.combined = c()
for ( i in allSampleName ) {
    print(i)
    j = i
    fileDIR2 = paste(workDIR, i, "/outs/filtered_feature_bc_matrix", sep="")
    Data_tmp<-Read10X(data.dir = fileDIR2)
    Object32 <- CreateSeuratObject(counts = Data_tmp, project = j)
    
Object32@meta.data$Pt <-    samplePDX[samplePDX$scSeqName %in% i,]$Pt   ######################################
Object32@meta.data$sample <-    samplePDX[samplePDX$scSeqName %in% i,]$scSeqName
Object32@meta.data$Newname <-    samplePDX[samplePDX$scSeqName %in% i,]$Newname 
Object32@meta.data$HumanMouse <-    samplePDX[samplePDX$scSeqName %in% i,]$HumanMouse
Object32@meta.data$PDXmodel <-    samplePDX[samplePDX$scSeqName %in% i,]$PDXmodel

Object32[["percent.mt"]] <- PercentageFeatureSet(Object32, pattern = "^MT-")
   outputName12 = paste0(outputDIR,"/qc/", i, ".VlnPlot_before_filter.png")
    png(outputName12,height =480, width = 960)
       print(VlnPlot(Object32, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3))
    dev.off()

Object32 <- NormalizeData(Object32)
Object32 <- FindVariableFeatures(Object32, selection.method = "vst", nfeatures= 2000)
Object32 <- ScaleData(Object32)

Object32 <- subset(Object32, subset = nFeature_RNA > 200 & nFeature_RNA < 6000 & percent.mt < 10)
Object32    

outputName12 = paste0(outputDIR,"/qc/", i, ".VlnPlot_after.png")
png(outputName12,height =480, width = 960) 
print(VlnPlot(Object32, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3) )
dev.off() 
   Object.combined = c(Object.combined, Object32)

  }
```

```{r}
#c("A","B","D")
  Object.all <- merge(Object1, y =   Object.combined, add.cell.ids =c(initialSampleName, allSampleName)  , project = "SC145")
  Object.all <- NormalizeData(object = Object.all, verbose = FALSE)
  Object.all <- ScaleData(Object.all)
  Object.all <- FindVariableFeatures(object = Object.all, selection.method = "vst", nfeatures = 2000)
  Object.all <- RunPCA(Object.all, features = VariableFeatures(object = Object.all))
  saveRDS(Object.all, "/data/exx/SC/SC145/Data/Object1.CQS.rds")

```

```{r}
Objectall <- readRDS( "/data/exx/SC/SC145/Data/Object1.CQS.rds")
Objectall<- Object.all
Objectall <- RunHarmony(Objectall, "sample")
Objectall <- ScaleData(Objectall,verbose = FALSE)
Objectall <- RunUMAP(Objectall, reduction = "harmony", dims = 1:30)
Objectall <- FindNeighbors(Objectall, reduction = "harmony", dims = 1:30)
Objectall <- FindClusters(Objectall, resolution = 0.5)
saveRDS(Objectall, "/data/exx/SC/SC145/Data/Hamed.CQS.rds")

```

```{r}
Objectall <- readRDS( "Hamed.CQS.rds")
```


```{r}
Objectall <- RunTSNE(Objectall, reduction = "harmony", dims = 1:30)
#Objectall <- FindNeighbors(Objectall, reduction = "harmony", dims = 1:30)
#Objectall <- FindClusters(Objectall, resolution = 0.5)
saveRDS(Objectall, "Hamed.CQS.2.rds")
```

```{r,fig.height=10, fig.width= 10}
#str(Objectall)
#Objectall <- readRDS( "Hamed.CQS.2.rds")

dim(Objectall@meta.data)
samplePDX[,c("Finalname","scSeqName")]
Objectall@meta.data 
#dim(merge(Objectall@meta.data, samplePDX[,c("Finalname","scSeqName")], by.x="sample", by.y="scSeqName"))
Objectall@meta.data$row <- rownames(Objectall@meta.data)
Objectall@meta.data 
#Objectall@meta.data <-
 a <- merge(Objectall@meta.data, samplePDX[,c("Finalname","scSeqName")], by.x="sample", by.y="scSeqName")
 a
rownames(a) <- a$row
a
Objectall@meta.data <- a
```

```{r, fig.height=10, fig.width= 10, echo=FALSE, warning=FALSE, message=FALSE}}
p1 <- DimPlot(Objectall, reduction = "tsne", label = TRUE)
print(p1)
```

```{r,fig.height=12, fig.width= 12}
FeaturePlot(Objectall, features = c("CD79A", "CD79B","NKG7", "GNLY","S100A9", "HBB", "ZNF90","MCL1",
                                    "HIST1H4C", "TUBA1B", "TUBB", "PCLAF","TYMS"),reduction = "tsne", min.cutoff = "q9")
```


```{r,fig.height=55, fig.width= 18}
#cc_file <- getURL("https://raw.githubusercontent.com/hbc/tinyatlas/master/cell_cycle/Homo_sapiens.csv") 
cell_cycle_genes <- read.csv("Homo_sapiens.csv")
library(AnnotationHub)
library(ensembldb)
# Connect to AnnotationHub
ah <- AnnotationHub()

# Access the Ensembl database for organism
ahDb <- query(ah, 
              pattern = c("Homo sapiens", "EnsDb"), 
              ignore.case = TRUE)

# Acquire the latest annotation files
id <- ahDb %>%
        mcols() %>%
        rownames() %>%
        tail(n = 1)

# Download the appropriate Ensembldb database
edb <- ah[[id]]

# Extract gene-level information from database
annotations <- genes(edb, 
                     return.type = "data.frame")

# Select annotations of interest
annotations <- annotations %>%
        dplyr::select(gene_id, gene_name, seq_name, gene_biotype, description)

# Get gene names for Ensembl IDs for each gene
cell_cycle_markers <- dplyr::left_join(cell_cycle_genes, annotations, by = c("geneID" = "gene_id"))

# Acquire the S phase genes
s_genes <- cell_cycle_markers %>%
        dplyr::filter(phase == "S") %>%
        pull("gene_name")
        
# Acquire the G2M phase genes        
g2m_genes <- cell_cycle_markers %>%
        dplyr::filter(phase == "G2/M") %>%
        pull("gene_name")
```


```{r}
# Perform cell cycle scoring
Objectall <- CellCycleScoring(Objectall,
                                   g2m.features = g2m_genes,
                                   s.features = s_genes)

# Perform PCA and color by cell cycle phase
#Objectall <- RunPCA(Objectall)

# Visualize the PCA, grouping by cell cycle phase

DimPlot(Objectall,
        reduction = "tsne",
        group.by= "Phase")
DimPlot(Objectall,
        reduction = "umap",
        group.by= "Phase")
```


```{r, fig.height=10, fig.width= 18}
#p1 <- DimPlot(Objectall, reduction = "umap", group.by = "sample")
p1 <- DimPlot(Objectall, reduction = "tsne", group.by = "Finalname")

print(p1)
```

```{r,fig.height=55, fig.width= 18}
#DimPlot(Objectall, reduction = "tsne", split.by = "sample", label = TRUE, ncol =4)
DimPlot(Objectall, reduction = "tsne", split.by = "Finalname", label = TRUE, ncol =4)
```

```{r, fig.height=10, fig.width= 10, echo=FALSE, warning=FALSE, message=FALSE}}
p1 <- DimPlot(Objectall, reduction = "umap", label = TRUE)
print(p1)
```

Show in New WindowClear OutputExpand/Collapse Output
Registered S3 methods overwritten by 'htmltools':
  method               from         
  print.html           tools:rstudio
  print.shiny.tag      tools:rstudio
  print.shiny.tag.list tools:rstudio
Registered S3 method overwritten by 'data.table':
  method           from
  print.data.table     
Registered S3 method overwritten by 'htmlwidgets':
  method           from         
  print.htmlwidget tools:rstudio
package ‘ggplot2’ was built under R version 3.6.3package ‘readr’ was built under R version 3.6.3package ‘readxl’ was built under R version 3.6.3package ‘Matrix’ was built under R version 3.6.3
Attaching package: ‘Matrix’

The following object is masked from ‘package:S4Vectors’:

    expand

package ‘tidyr’ was built under R version 3.6.3
Attaching package: ‘tidyr’

The following objects are masked from ‘package:Matrix’:

    expand, pack, unpack

The following object is masked from ‘package:S4Vectors’:

    expand

package ‘cowplot’ was built under R version 3.6.3
********************************************************
Note: As of version 1.0.0, cowplot does not change the
  default ggplot2 theme anymore. To recover the previous
  behavior, execute:
  theme_set(theme_cowplot())
********************************************************

[1] "all.markers.rds"         "all.markers.txt"         "Hamed.CQS.rds"           "harmony.Rmd"             "PDX_scRNA_WES_info.xlsx" "seurat.yaml"            
Show in New WindowClear OutputExpand/Collapse Output
New names:                                                                                                                                                                                                                                      
* scRNA -> scRNA...6
* scRNA -> scRNA...19
  [1] "964301-B0"                  "964303-B1"                  "1106365-B4"                 "1106365"                    "B00  (1106365 TID CD19(-))" "249479-4-Liver"             "249479-4-LN"                "249479-4-Tumor"            
  [9] "249479-4-Spleen"            "249479-4-Stomach"           "285861-1-Tumor"             "285908-2-Tumor"             "285861-1-Spleen"            "318819-2-tumor"             "T7"                         "S7"                        
 [17] "398322-Tumor"               "398326-Tumor"               "407347-scTumor"             "439205-1-Tumor"             "439205-2-Tumor"             "181834-3-Liver"             "181834-3-Tumor"             "1818343-Spleen"            
 [25] "181834-4-Spleen"            "181834-3-Spleen"            "181834-3-Stomach"           "249471-4-BM"                "249472-1-BM"                "249471-4-Liv"               "249472-1-Liv"               "249469-1-Liver"            
 [33] "249471-4-PB"                "249472-1-PB"                "249474-1-Spleen"            "249471-4-spl"               "249472-1-Spl"               "249469-1-Spleen"            "249469-1-Stomach"           "249480-spleen"             
 [41] "285875-1-Spleen"            NA                           "286194-1-spleen"            "347720-1-spleen"            "S10"                        "382632-1-spleen"            "407348-Spleen"              "1215665"                   
 [49] "1216276"                    "318796-2-BM"                "318796-2-Liver"             "T3"                         "S3"                         "ST3"                        "382611-1-BM"                "382611-1-Liver"            
 [57] "382611-1-LN"                "382611-1-Spleen"            "1227142"                    "1228722"                    "312275-2-Tumor"             "382596-4-Tumor"             "382596-4-Spleen"            "347796-3-Tumor"            
 [65] "347795-Tumor"               "407359-4-BM"                "407359-4-Liver"             "407321-1-Tumor"             "407324-scTumor"             "407359-3-Tumor"             "407359-4-Spleen"            "439216-tumor"              
 [73] "318871-2-Liver"             "T6"                         "318871-2-Spleen"            "1245334"                    "1245334-CD3-T-cells"        "347793-2-BM"                "347793-2-Liver"             "347793-2-Tumor"            
 [81] "347793-2-Spleen"            "1246565"                    "1247166-saliva"             "347797-2-BM"                "347797-2-Liver"             "347797-2-Spleen"            "347797-2-Uterus"            "382636-Spleen"             
 [89] "1264446"                    "1301991-saliva"             "407289-4-BM"                "407289-4-Liver"             "407289-4-Tumor"             "407289-4-Spleen"            "PBMC-1"                     "PBMC-2"                    
 [97] "407348-Blood"               "407348-BM"                  "407348-Liver"               "347795-Blood"              
R Console
WESinformation
<chr>
NA	
NA	
Shaojun has for PT scRNA project MRN 2011102; TID 1106365	
WES Batch 1	
Shaojun has for PT scRNA project	
WES Batch 2	
WES Batch 2	
WES Batch 2	
WES Batch 2	
WES Batch 2	
Next123456...11Previous
1-10 of 102 rows | 1-1 of 20 columns
data.frame
102 x 20
WESinformation
<chr>
SMFname
<chr>
Oldname
<chr>
scSeqName
<chr>
Finalname
<chr>
scRNA...6
<chr>
old_Samplename
<chr>
NA	NA	NA	964301-B0	A00	scRNA	NA	
NA	NA	NA	964303-B1	A01	scRNA	NA	
Shaojun has for PT scRNA project MRN 2011102; TID 1106365	NA	B4	1106365-B4	A0	scRNA	B4 (1106365 TID)	
WES Batch 1	NA	PT_1106365	1106365	A0	NA	1106365	
Shaojun has for PT scRNA project	NA	B00	B00 (1106365 TID CD19(-))	A0-germline	NA	B00 (1106365 TID CD19(-))	
WES Batch 2	PDX_24	NA	249479-4-Liver	AS_G2_LI	NA	249479-4-Liver	
WES Batch 2	PDX_22	NA	249479-4-LN	AS_G2_LN	NA	249479-4-LN	
WES Batch 2	PDX_7	NA	249479-4-Tumor	AS_G2_SC	scRNA	249479-4-Tumor	
WES Batch 2	PDX_21	NA	249479-4-Spleen	AS_G2_SP	scRNA	249479-4-Spleen	
WES Batch 2	PDX_23	NA	249479-4-Stomach	AS_G2_ST	NA	249479-4-Stomach	
Next123456...11Previous
1-10 of 102 rows | 1-7 of 20 columns
Show in New WindowClear OutputExpand/Collapse Output


```{r, fig.height=10, fig.width= 18}
#p1 <- DimPlot(Objectall, reduction = "umap", group.by = "sample")
p1 <- DimPlot(Objectall, reduction = "umap", group.by = "Finalname")

print(p1)
```
```{r, fig.height=15, fig.width= 20}
p1 <- DimPlot(Objectall, reduction = "umap", group.by = "Pt")
print(p1)
```

```{r}
#all.markers  <- FindAllMarkers(Objectall, only.pos = T, min.pct = 0.01, logfc.threshold = 0.25)
#saveRDS(all.markers,"/data/exx/SC/SC145/Data/all.markers.rds")
#write.table(all.markers, "/data/exx/SC/SC145/Figure.CQS/all.markers.txt")
all.markers <- readRDS("all.markers.rds")
```

```{r,fig.height=55, fig.width= 18}
DimPlot(Objectall, reduction = "umap", split.by = "sample", label = TRUE, ncol =4)
DimPlot(Objectall, reduction = "umap", split.by = "Finalname", label = TRUE, ncol =4)
```
c("LTB", "CD79A", "CD79B", "CD52", "CD37", 
                "HIST1H4C", "TUBA1B", "TUBB", "PCLAF","TYMS",
  "PKM", "GNLY", "NKG7", "SAA1", "ZNF90", "CCL3", "S100A9", "S100A8", "HIST3H2A", "HBB", "HBD")
#RidgePlot(Objectall, features = features, ncol = 3)

```{r,fig.height=8, fig.width= 10}
for (i in 0:15) {
features <- all.markers[all.markers$cluster %in% i,]$gene[1:10]
print(DotPlot(Objectall, features = features) + RotatedAxis())
}


```

```{r,fig.height=8, fig.width= 10}
features <- all.markers[all.markers$cluster %in% "1",]$gene[1:10]
DotPlot(Objectall, features = features) + RotatedAxis()
```

```{r,fig.height=8, fig.width= 10}
features <- all.markers[all.markers$cluster %in% "2",]$gene[1:10]
DotPlot(Objectall, features = features) + RotatedAxis()
```

Bcell gene
```{r,fig.height=5, fig.width= 5}
FeaturePlot(Objectall, features = c("CD79A", "CD79B","GZMA", "MS4A1"), min.cutoff = "q9")
```

```{r,fig.height=12, fig.width= 12}
FeaturePlot(Objectall, features = c("CD79A", "CD79B","NKG7", "GNLY","S100A9", "HBB", "ZNF90","MCL1",
                                    "HIST1H4C", "TUBA1B", "TUBB", "PCLAF","TYMS"), min.cutoff = "q9")
```



```{r,fig.height=55, fig.width= 18}
#cc_file <- getURL("https://raw.githubusercontent.com/hbc/tinyatlas/master/cell_cycle/Homo_sapiens.csv") 
cell_cycle_genes <- read.csv("Homo_sapiens.csv")
library(AnnotationHub)
library(ensembldb)
# Connect to AnnotationHub
ah <- AnnotationHub()

# Access the Ensembl database for organism
ahDb <- query(ah, 
              pattern = c("Homo sapiens", "EnsDb"), 
              ignore.case = TRUE)

# Acquire the latest annotation files
id <- ahDb %>%
        mcols() %>%
        rownames() %>%
        tail(n = 1)

# Download the appropriate Ensembldb database
edb <- ah[[id]]

# Extract gene-level information from database
annotations <- genes(edb, 
                     return.type = "data.frame")

# Select annotations of interest
annotations <- annotations %>%
        dplyr::select(gene_id, gene_name, seq_name, gene_biotype, description)
```
```{r}
# Get gene names for Ensembl IDs for each gene
cell_cycle_markers <- dplyr::left_join(cell_cycle_genes, annotations, by = c("geneID" = "gene_id"))

# Acquire the S phase genes
s_genes <- cell_cycle_markers %>%
        dplyr::filter(phase == "S") %>%
        pull("gene_name")
        
# Acquire the G2M phase genes        
g2m_genes <- cell_cycle_markers %>%
        dplyr::filter(phase == "G2/M") %>%
        pull("gene_name")
```


```{r}
# Perform cell cycle scoring
Objectall <- CellCycleScoring(Objectall,
                                   g2m.features = g2m_genes,
                                   s.features = s_genes)

# Perform PCA and color by cell cycle phase
#Objectall <- RunPCA(Objectall)

# Visualize the PCA, grouping by cell cycle phase
DimPlot(Objectall,
        reduction = "umap",
        group.by= "Phase")
```

```{r, fig.height=55, fig.width= 18}
DimPlot(Objectall,
        reduction = "umap",
        group.by= "Phase", split.by = "Finalname", ncol= 4)

```


features <- c("GNLY", "NKG7")
RidgePlot(Objectall, features = features, ncol = 2)
```


#for anchoring
pdx.list <- SplitObject(Object.all, split.by = "sample")
saveRDS(pdx.list, file = "/data/exx/SC/SC145/Data/0.pdx.list.rds")

for (i in 1:length(pdx.list)) {
    pdx.list[[i]] <- NormalizeData(pdx.list[[i]], verbose = FALSE)
    pdx.list[[i]] <- FindVariableFeatures(pdx.list[[i]], selection.method = "vst", nfeatures = 2000, verbose = FALSE)
}

pdx.anchors <- FindIntegrationAnchors(object.list = pdx.list, dims = 1:30)
saveRDS(pdx.anchors, file= "/data/exx/SC/SC145/Data/1.pdx.anchors.rds")

```

```{r}
pdx.anchors <- readRDS("/data/exx/SC/SC145/Data/1.pdx.anchors.rds")

```
```{r}
library(future)
plan("multiprocess", workers =4)
pdx.integrated <- IntegrateData(anchorset = pdx.anchors, dims = 1:30)          
saveRDS(pdx.integrated, file= "/data/exx/SC/SC145/Data/2.pdx.integrated.rds")



```





